\ifdefined\COMPLETE
\else
	\input{../definitions.tex}
	\begin{document}
\fi

\def\pagetitletext{Welcome to WONDERFUL STORIES}

Hello! Thank you for picking up a copy of our booklet!\\

We’re super excited to release this booklet to support the first large-scale \textbf{Delayed Viewing} (or DV for short) of an Aqours concert in Europe! Today, you'll see the first leg of their third Live Tour, \textbf{"WONDERFUL STORIES"}, recorded at the MetLife Dome in Saitama on June 9th 2018.\\

What you have in your hand right now will be your "little helper" for the event. Whether you’re unfamiliar with Love Live or a die-hard fan since the beginning, this book explains all of the calls, the Do’s and Don'ts of a live and provides the setlist for today's screening!\\

The first part will introduce you to \textbf{calls}, a way to support performers on stage during the live and to unite with the other attendees to cheer on Aqours. The second half of this booklet will list \textbf{lyrics and call guides} for all the songs in the live, so you can join in with everyone!\\

We hope you will enjoy the screening! Aqours... Sunshine!!\\
\vspace{\fill}\\
\textbf{\large \colorstring{Who Are Aqours?}}\\

Aqours is the second idol group in the "Love Live!" franchise, a multimedia project centered around nine girls who start an idol club at their school. Developed by Dengeki G’s magazine, music publisher Lantis and animation studio Sunrise back in 2010, the series has grown ever since and has a fan following all around the world.\\

Aqours debuted in 2015 in the "Love Live! Sunshine!!" series. With two anime seasons, an upcoming movie and three major live concerts, this group has grown at an exponential pace. Each of the nine performers represents one of the characters on the stage, bringing the songs and scenes from the series to life.
\vspace{\fill}

\ifdefined\COMPLETE
\else
	\end{document}
\fi